%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                           % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Simon}{Zeng}
% \title{Computer Science Student}                               % optional, remove / comment the line if not wanted
\phone[mobile]{+1~(613)~983~9079}                   % optional, remove / comment the line if not wanted
\email{simon.zeng@uwaterloo.ca}                               % optional, remove / comment the line if not wanted
% \homepage{www.s-zeng.github.io}                         % optional, remove / comment the line if not wanted
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Shopify Recruitment Team}{Shopify, Inc.\\150 Elgin Street\\Ottawa, 
    Ontario}
\date{January 18, 2019}
\opening{Dear Marylou,}
\closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Perhaps the number one purpose of a cover letter is an exchange between two 
parties - the employer seeks something that can characterize a great candidate, 
and the applicant wishes to convince the employer that he/she is the great 
candidate that they've been seeking. And since the resume already exists as a 
succinct summary of qualifications, it should be the cover letter's job to 
expand and fill in any gaps to be found in the resume. To that end, I find it 
useful skip all the stiff formalism that conventionally surrounds cover letters, 
and jump straight into the desired exchange of information.

With regard to my ability to perform well in this position:
\smallskip
\begin{enumerate}
    \item I have a \textbf{strong interest and enthusiasm in mathematics and 
            problem solving}. With high grades in my advanced level math 
        courses, multiple accolades in a variety of competitions, and a genuine 
        hobbyist affinity towards puzzles, I believe that my mindset will be 
        perfectly suited for tackling the problems that a Backend Developer, 
        Security Engineer, or Software Engineer Intern at Shopify will face.
        \smallskip
    \item I possess a \textbf{modest amount of experience}. In particular, I 
        believe that my prior work in Ruby on Rails at inBay, in conjunction 
        with my knowledge of network protocol debugging from CENX will make me 
        an immediate strong starter at Shopify in the event that I am accepted 
        into an applicable position.
        \smallskip
    \item I'm consistently \textbf{stubborn and curious}. It is this trait that 
        drove me to call out security issues and non-standards compliance at 
        CENX; it is this trait that made my solution to the production challenge 
        as minimal as can be, and it is for this reason why this application is 
        still in your hands this year, despite two consecutive rejections in the 
        past.
\end{enumerate}

I understand that there will be a large number of applications for this 
position. However, it is my belief that these outlined characteristics will 
enable me to best integrate with the culture at Shopify, and to immediately 
become an asset upon starting. I hope that this letter served its purpose as a 
knowledge transaction, and that your consideration of my candidacy has been 
appropriately adjusted for it.
\smallskip

Thanks in advance for your time,

\textbf{Simon Zeng}

% \makeletterclosing

\end{document}


%% end of file `template.tex'.
